### 2022-06-24 Additional Problems/PARAFAC and Tensor Rank/manuscript.tex
Updating L2 Q3

        \begin{align}
            \mathcal{S} = \sum^{R}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{s}^{(3)}_{r},
        \end{align}

@@

        We also know from the previous problem that the tensor rank is indeed a property. Thus, the tensor $\mathcal{X}$ and the core tensor $\mathcal{S}$ of its multilinear transformation will have the same tensor rank.
        Now, we only need to proof that either one of them are a tensor with rank three. The easiest way to do this is by working with the core tensor of the multilinear transformation, the tensor $\mathcal{S}$, and start a proof by contradiction.

>>>>

        \begin{align}
            \mathcal{S} = \sum^{R}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{s}^{(N)}_{r},
        \end{align}

@@

        We also know from the previous problem that the tensor rank is indeed a property. Thus, the tensor $\mathcal{X}$ and the core tensor $\mathcal{S}$ of its multilinear transformation will have the same tensor rank.
        Now, we only need to proof that either one of them are a tensor with rank three. The easiest way to do this is by working with the core tensor of the multilinear transformation, the tensor $\mathcal{S}$, and start 
        a proof by contradiction defining that $rank(\mathcal{S}) = 2$. This means that we can write the PARAFAC Decomposition of this tensor assunto

        \begin{align}
            \mathcal{S} = \sum^{2}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \boldsymbol{s}^{(2)}_{r} \circ \boldsymbol{s}^{(3)}_{r},
        \end{align}

### 2022-06-24 Report/manuscript.tex
Updating L2 Q3

@@

    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones. This is simply explained by 
    the scale ambiguity intrinsic to the MLS-KronF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.
    It is also important to say that the produced algorithm was generalized for a random number of factors.

@@

    \begin{figure*}
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
            \centering
            \includegraphics[width=\textwidth]{figs/hw10a1.png} 
            \caption[]%
            {{\small Scenario 1}}    
            \label{fig:hw10a1} 
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.475\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{figs/hw10a1.png} 
            \caption[]%
            {{\small Scenario 2}}    
            \label{fig:hw10a2} 
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{figs/hw10a3.png} 
            \caption[]%
            {{\small Scenario 3}}    
            \label{fig:hw10a3} 
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{figs/hw10a4.png} 
            \caption[]%
            {{\small Scenario 4}}    
            \label{fig:hw10a4} 
        \end{subfigure}
        \caption[Monter Carlo Experiment with 1000 runs for MLS-KronF algorithm.]
        {\small Monter Carlo Experiment with 1000 runs for MLS-KronF algorithm.} 
        \label{fig:mean and std of nets}
    \end{figure*}

>>>>

    and by implementing the algorithm it was possible to reach the following table of NMSE (dB) values using the validation files 
    for the HOSVD and HOOI initialization, respectively.

@@

    \begin{table}[ht!]
        \centering
        \begin{tabular}{|l|l|l|l|}
        \hline
        NNMSE($\boldsymbol{X}, \boldsymbol{\hat{X}}$) & NMSE($\boldsymbol{A}_{1}, \boldsymbol{\hat{A}}_{1}$) & NMSE($\boldsymbol{A}_{2}, \boldsymbol{\hat{A}}_{2}$) & NMSE($\boldsymbol{A}_{3}, \boldsymbol{\hat{A}}_{3}$) \\ \hline
        -608.4705 & +5.4597 & +15.0478 & +5.8977 \\ \hline
        \end{tabular}
    \end{table}

    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones for both cases. This is simply explained by 
    the scale ambiguity intrinsic to the MLS-KronF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.
    It is also important to say that the produced algorithm was generalized for a random number of factors.

@@

    \begin{figure*}
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
            \centering
            \includegraphics[width=\textwidth]{figs/hw10a1.png} 
            \caption[]%
            {{\small Scenario 1}}    
            \label{fig:hw10a1} 
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.475\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{figs/hw10a2.png} 
            \caption[]%
            {{\small Scenario 2}}    
            \label{fig:hw10a2} 
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{figs/hw10a3.png} 
            \caption[]%
            {{\small Scenario 3}}    
            \label{fig:hw10a3} 
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{figs/hw10a4.png} 
            \caption[]%
            {{\small Scenario 4}}    
            \label{fig:hw10a4} 
        \end{subfigure}
        \caption[Monter Carlo Experiment with 1000 runs for MLS-KronF algorithm.]
        {\small Monter Carlo Experiment with 1000 runs for MLS-KronF algorithm.} 
        \label{fig:mean and std of nets}
    \end{figure*}
